---
output: github_document
editor_options: 
  chunk_output_type: console
---


# flighttools

<!-- badges: start -->
<!-- badges: end -->

`flighttools` is a personal package for Robert M Flight, with some functions that I find
myself needing regularly.
Nothing in it is meant to be **required** for an analysis, so that this package doesn't **need** to
be installed for something to run.
Instead, most of the functions are helpers, either providing interactive functionality, or providing
code that I can paste somewhere else to do something.

If you like the functions and want to use them as is, go ahead and install the package.
I actually recommend that you fork this package, or look over the code and borrow what you want
to make your own.
Everything is MIT licensed, so go for it.

## Installation

You can install the development version of `flighttools` from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("rmflight/flighttools")
```

## Notifiers

The functions I use the most are probably the notification functions.
There are three, for slightly different use cases, but they all work roughly the same way:

``` r
library(flighttools)
ft_*_success_error(code_to_evaluate)
```

- `ft_beep_success_error`: plays a sound from `beepr` if code is successful, a different one if there is an error;
- `ft_notify_success_error`: creates a visual notification using `notify-send` on linux;
- `ft_ntfy_success_error`: sends a network notification using the `ntfy` [package](https://github.com/jonocarroll/ntfy).

I typically use these when I am running a long function, or when I am running `targets` pipelines.
What is really nice, is they take whatever R code you supply, evaluate it, and then check if the code errored.
If it didn't error, it just returns the results.
If it errored, it tells you, by changing the notification, and then returns the results.

```{r}
#| label: example-notification
#| eval: false
ft_beep_success_error(tar_make())
ft_beep_success_error(tar_make(valid_target_name))
```

## Markdown Code Helpers

Many functions just spit code into the terminal for me to copy into a document or code file.
For example, I have a title block I use regularly.
It's not enough for me to have a template, but I do like to use a consistent one.
This way, I can have this package installed, but not as a hard dependency, and just copy the output into a project Rmd or qmd file.

```{r}
#| label: example-title
#| comment: ""
library(flighttools)
ft_title_block()
```

## Graphics Code Helpers

Do you remember the code to turn axis labels 90 degrees in a `ggplot2` graph?
Me neither.
But this gives me the code to add to a plot.

```{r}
#| label: ggplot2-90
ft_rotate_axis_labels()
```

## File Manipulation

When I'm using `targets`, I also like to be able to rename file outputs with the current date, so I can keep track of versions, as well as zip the Word figure directory up to share with others.

```{r}
#| label: file-manipulators
#| eval: false
ft_rename_outputs(tar_read(file_output), prefix = "initials_info")
ft_zip_directory("docs/file_output/figure-docx", "docs/file_output_figures.zip")
```
